\chapter{Procedures and Deadlines}
\label{app:procedures}

\paragraph{Deadlines}

At least one semester prior to the semester in which you believe you will
complete all requirements for your degree, please be sure to consult with your
department’s graduate administrative assistant or coordinator to be sure you
are aware of all requirements and deadlines with regards to the submission of
your thesis or dissertation.  Deadlines are printed in the course listings
schedule book and are posted online.  If you cannot make certain deadlines, you
may have to postpone your graduation accordingly.  In particular, a student
must file an ``intent to graduate'' form (via WebSTAC) by the published
deadline prior to any anticipated graduation date; otherwise, no degree can be
earned.  M.S.\ and D.Sc.\ students also have a special deadline by which they
must submit an initial hard copy draft of their thesis to Engineering Student
Services in Lopata 303 so that it can be reviewed for formatting.  After a
draft has been submitted for format review, an email will be sent to you within
48 hours detailing any changes that need to be made in the formatting of your
thesis or dissertation.  For M.S.\ and D.Sc.\ students, approval of your thesis
or dissertation formatting must be received prior to turning in the final
electronic and hard copy versions as described below.  

Ph.D.\ students must follow the requirements of the Office of Graduate Students
in Arts and Sciences (GSAS).  The GSAS office does not have special formatting
deadlines, but you should still contact that office if you have questions about
your formatting.

\paragraph{Oral Examination}

Each member of the oral examining committee must be given a copy of the thesis
or dissertation, in final form, in sufficient time to study it before the oral
examination.  Members of the examining committee have the right to request
rescheduling of the examination if these copies are not made available to them
at least one week in advance of the scheduled examination date.  Copier paper
may be used for these preliminary copies.

\paragraph{Electronic Submission}

After the oral defense, an M.S.\ or D.Sc.\ student is required to submit an
electronic version of his/her final thesis or dissertation in PDF format.  The
links can be found on the School of Engineering website under Information for
Graduate Students.   Click on the link for Thesis Submissions to submit a
Master's Thesis or click on the link for Dissertation Submissions to submit a
Doctoral Dissertation. The website for doctoral students submitting
dissertations requires students to choose among publishing and copyrighting
services offered, but the University permits students to make whichever choices
they prefer. Doctoral students are asked to submit a Survey of Earned
Doctorates separately to Engineering Student Services. 

Please note that the electronic submission of your thesis or dissertation
should be made by the stated deadline date on the current academic calendar and
prior to handing in the final hard copies as described below.  An administrator
in Engineering Student Services will review the electronic copy of your thesis
or dissertation and officially approve the submission online.  This electronic
version will be used for library publication and catalog purposes. In addition,
students typically must submit hard copies of the thesis or dissertation for
binding purposes (see below).  

\paragraph{Final Hard Copies}

After the oral defense and electronic submission, final copies of the thesis or
dissertation approved by the examination committee and department are to be
submitted to Engineering Student Services in Lopata 303 on or before the date
stated in the current academic calendar.

\begin{enumerate}
	\item	
	\textbf{Three} final copies (unless your department instructs you
	otherwise) must be printed using only one side on 8.5 $\times$ 11 inch
	white paper and minimum 20-pound weight. (Most printer and copier paper
	qualify, but a high-quality watermarked or 10--25\% cotton paper is
	recommended.) Print should be letter quality.  Copies submitted should
	\uline{not} be bound, stapled, clipped or hole-punched.  To avoid
	delays in publication, please make certain that the copies you submit
	include all pages of your thesis or dissertation.
	
	Each copy should be placed in a separate unsealed manila envelope with
	a copy of the \textbf{short title page} (see description below)
	securely taped to the outside of each envelope.

	\begin{list}{}{}
		\item \textit{%
		Engineering Student Services sends all three copies of your
		thesis or dissertation to West Campus Library.  The Library
		will have these copies professionally bound and sent back to
		your home department.  The home department will keep one copy
		and distribute one to your advisor.  The third copy will be
		mailed to you at your home address.  In order for you to
		receive your bound thesis or dissertation promptly, your home
		department must have your current mailing address.  On your
		``intent to graduate'' form you should input your ``address
		after graduation.''   Processing theses and dissertations takes
		time, so you may have to wait 3--6 months after your graduation
		date to receive your copy. 
		}
	\end{list}

	\item		
	\uline{\textbf{Short Title} page is a loose sheet containing} (1) a
	\uline{short title} of 35 letters or less (including spaces), (2) the
	author’s last name, (3) the degree, and (4) the year of its award,
	centered on the page and punctuated as in the example.\footnote{See the
	sample short title page for this document}    This short title sheet is
	to be taped securely to the outside of each manila envelope as
	described above.  This information lets the bindery know what to put on
	the spine of the bound copies.  The title will be truncated if longer
	than 35 characters.
	
	\item
	\textbf{Doctoral (D.Sc.) degree candidates} must complete the Survey of
	Earned Doctorates form and submit it with the 3 copies of your final
	dissertation. You can download the Survey of Earned Doctorates form
	from the School of Engineering's website under Graduate Student
	Information and Forms.

	\textbf{NOTE FOR PH.D.\ STUDENTS}:  Deliver all three copies of your
	dissertation to the GSAS Office.  See GSAS dissertation guidelines on
	their web site.
\end{enumerate}

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "thesis-main"
%%% End: 
