\chapter{Citing References}
\label{cpt:citation}

In the References section at the end of your thesis, list references cited
using the style recommended in \textit{The Chicago Manual of
Style}~\cite{ChicagoManual} or another style acceptable to your committee.
Insert parenthetical references where the reference material is referred to in
the text.  This chapter explains how to format references according to
\textit{The Chicago Manual of Style}.  If you use a different style, you should
obtain the appropriate style rules.  For example, most journals periodically
print instructions for authors that include reference style rules.

\section{Parenthetical References}

References should be cited at the position in the text where they are noted.
\textit{The Chicago Manual of Style}~\cite{ChicagoManual} recommends two
systems for citations.  You may use either of these systems or an alternative
system acceptable to your committee.

\subsection{Author-Date System}

In this system, the last name of the author and the year of
publication appear in parentheses following the quoted text.  If the
reference is alphabetized in the References section by its editor,
publisher, or organization, then the name it is alphabetized under is
used in place of the author.  Some examples follow:
\begin{itemize}
 \item Single author: (Smith 1993)
 \item Two authors: (Jones and Yang 1991)
 \item Three authors: (Jones, Smith, and Yang 1984)
 \item Four or more authors: (Johnson et al. 1994)
 \item Organization as author: (Association for Computing Machinery 1989)
 \item Two works referenced in one sentence: (Black 1994; Smith 1993)
\end{itemize}

\subsection{Numbered References}

In this system, the reference number appears in square brackets following the
quoted text.  This system is used throughout this document.

\section{Reference List}

References should be listed in alphabetical order by the last name of the first
author (or organization or publisher, if no author is given).  If the numbered
reference style is used, the reference list should obviously be numbered as
well.  Several example references are listed in this document's reference list.
Most of these references are taken from \textit{A Manual for Writers of Term
Papers, Theses, and Dissertations}~\cite{Turabian}.

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "thesis-main"
%%% End: 
